Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-29 paper.tex
fixed Lemma 6

Since we are at round $n$, we know there exists at least one arm, which has been pulled exactly $n$ times. Without loss of generality, we assume it to be arm $1$. Since $P\left(|\epsilon_{i,t}^{j}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)> P\left(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right)$ for all $i,j$, we know

\begin{align}
\eqref{prob:upper}&\leq P\left(|\epsilon_{1,t}^{1}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)-P\left(|\epsilon_{1,t}^{1}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
=&P\left(\frac{l-1}{n}<|\epsilon_{1,t}^{1}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
=&P\left(\frac{\sqrt{n}(l-1)}{n}<|N(0,1)|<\frac{\sqrt{n}l}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
=&2\Phi\left(\frac{\sqrt{n}l}{n}\right)-2\Phi\left(\frac{\sqrt{n}(l-1)}{n}\right) \nonumber \\
=&2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}. \nonumber
\end{align}

Thus,
\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
\leq & \sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]\times 2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}Nn. \nonumber \\
\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2n}\right)\sqrt{n}. \nonumber
\end{align}

Denote $k_n=\max\{n_2, \lceil a_0 l \rceil\}$. Then we know
\begin{align}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]\exp\left(-\frac{(l-1)^2}{2k_n}\right)\sqrt{k_n} \nonumber \\
\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\left[R+2Wml\right]\exp\left(-\frac{(l-1)^2}{2k_n}\right)(k_n)^{3/2}=O(N). \nonumber
\end{align}

@@

\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative expected number of payments is bounded above by:
\begin{align}
&E[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}] \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}P\left(\exists i,j:|u_{i}^{j}-u_{i,t}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2m}\right)+\sum_{n=1}^{n_1}N \nonumber \\
\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn+\sum_{n=1}^{n_1}N \nonumber  \\
=&24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2} + Nn_1, \nonumber
\end{align}

>>>>

@@

\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|< \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2mW\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|< \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms. In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$. Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$. Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative expected number of payments is bounded above by:

Define $\tau_{n}^{k}$ to be a stopping time which equals to the $k_{th}$ time period in the $n^{th}$ round. Then
\begin{align}
&\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} \nonumber \\
=&\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}\sum_{t=k}^{\infty}\mathbbm{1}\{c(t)>0\}\mathbbm{1}\{t=\tau_{n}^{k}\} \nonumber 
\end{align}

Thus, we know
\begin{align}
&E[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}] \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\sum_{k=1}^{\infty}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{k}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)P(t=\tau_{n}^{k})+\sum_{n=1}^{n_1}N \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\sum_{k=1}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times P(t=\tau_{n}^{k})+\sum_{n=1}^{n_1}N \nonumber \\
\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn+\sum_{n=1}^{n_1}N \nonumber  \\
=&24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2} + Nn_1, \nonumber
\end{align}
